\textbf{Volatility and the Buyback Anomaly}

### 2016-05-15 index.Rmd
minor rename

source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
source("interactive_tool_files/ff_industries_sic.R")
source("Paper_global_parameters.R")
source("interactive_tool_files/heatmapOutput.R") 
source("interactive_tool_files/ff_industries_sic.R")

>>>>

source("library_files/lib_helpers.R", chdir=TRUE)
source("library_files/ff_industries_sic.R")
source("Paper_global_parameters.R")
source("library_files/heatmapOutput.R") 
source("library_files/ff_industries_sic.R")

### 2016-05-15 manuscriptJF.Rnw
test
almost final
minor
minor rename

@@

source("interactive_tool_files/lib_helpers.R", chdir=TRUE)
source("interactive_tool_files/latex_code.R")
source("interactive_tool_files/ff_industries_sic.R")
source("Paper_global_parameters.R")

@@

\vspace{-.2in}
\begin{abstract}
\noindent  We find that, inconsistent with the low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high. This is consistent with \cite{Stambaugh2015} who find a positive relation between returns and idiosyncratic volatility for undervalued stocks, and with the prediction that a repurchase authorization is an option for undervalued stocks \citep{IkenberryVermaelen1996}. The buyback anomaly also survives  when using the five-factor model of Fama and French (2015a).  Combining volatility with undervaluation indicators proposed by \cite{PeyerVermaelen2009} improves the predictive power of excess returns after buyback announcements.
\end{abstract}
\vspace{2cm}

>>>>

%  Copyright 2015, INSEAD
%  by T. Evgeniou, Enric Junque de Fortuny, Nick Nassuphis, Theo Vermaelen 
%  Dual licensed under the MIT or GPL Version 2 licenses.

@@

source("library_files/lib_helpers.R", chdir=TRUE)
source("library_files/latex_code.R")
source("library_files/ff_industries_sic.R")
source("Paper_global_parameters.R")

@@

\vspace{-.2in}
\begin{abstract}
\noindent  We find that, inconsistent with the low volatility anomaly, post-buyback announcement long-term abnormal returns are higher when the pre-announcement (idiosyncratic) volatility is high. This is consistent with \cite{Stambaugh2015} who find a positive relation between returns and idiosyncratic volatility for undervalued stocks, and with the prediction that a repurchase authorization is an option for undervalued stocks \citep{IkenberryVermaelen1996}. The buyback anomaly also survives  when using the five-factor model of Fama and French (2015a).  Combining volatility with undervaluation indicators proposed by \cite{PeyerVermaelen2009} improves the predictive power of excess returns after buyback announcements.

\end{abstract}
\vspace{2cm}

\noindent An interactive online tool to explore data variations and robustness analyses of all results in this paper, as well as all the source code, is available at \href{http://tevgeniou.github.io/BuybacksIssuers/}{tevgeniou.github.io/BuybacksIssuers.}
